\cvsection{Projects}
\begin{cventries}
  \cventry
    {Formal Concept Analysis Project}
    {Data Mining-Modification of ECLAT/LCM algorithms}
    {IIT Mandi}
    {July. 2017 - Ongoing}
    {
      \begin{cvitems}
        \item {Worked on modifying the ECLAT / LCM algorithm by Dr. Christian Borgelt to work on
distributed systems. The algorithm is used to mine Formal Concepts to build concept
lattices.}
        \item {Made programs and scripts to test the algorithm on larger dataset. }
        \item {Generated boolean context from the CSV file to mine Formal Concepts from it. }
        \item {Given the task to parse JSON file to CSV such that concepts could be mined from it. }
      \end{cvitems}
    }
  \cventry
    {PANDORA - Music Streaming Website(Ruby on Rails)}
    {Academic Project for Advanced Database Practicum Course }
    {IIT Mandi}
    {3rd Semester}
    {
      \begin{cvitems}
        \item {Developed this website using Ruby on Rails framework and MySQL database. Responsible for front-end, database schema and helped with back-end.}
      \end{cvitems}
    }
  \cventry
    {Classification of Library Books}
    {Project on implementation of Formal Concept Analysis}
    {Central Library, IIT Mandi}
    {June 2017 - July 2017}
    {
      \begin{cvitems}
        \item {Built a concept lattice of library books using Orient DB for a more meaningful classification and arrangement.}
      \end{cvitems} 
    }
  \cventry
    {Voice controlled pick and place robot}
    {Using Arduino and AVR shield}
    {Inter-IIT Tech-Meet}
    {2nd Semester, Jan. 2016- Feb. 2016}
    {
      \begin{cvitems}
        \item {Won 3rd Prize in the robotics event of Inter-IIT Tech Meet.}
        \item {Worked on the program(written in C) and training of the AVR shield.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
      \cventry
    {Pattern Recognition Models/Classifier}
    {Built as Coursework}
    {IIT Mandi}
    {Aug. 2017 - Ongoing}
    {
      \begin{cvitems}
        \item {Built Bayesian, K-Means Clustering and Gaussian Mixture Models classifiers for assignments using python libraries(pandas, numpy, scipy, sci-kit learn).}
      \end{cvitems}
    }
     \cventry
    {The Solar Labs}
    {Front-end and Webmaster}
    {Mandi, H.P.}
    {Feb. 2016- June. 2016}
    {
      \begin{cvitems}
        \item {Developed the front-end of the main website and customer management system.}
        \item {Set up a WordPress blog for the Start-Up.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
    \cventry
        {Tic-Stack-Toe}
    {Two player CLI game made in first semester}
    {IIT Mandi}
    {Aug. 2015- Sep. 2015}
    {
    \begin{cvitems}
    \item {Interactive command line game written in C with a colorful interface.}
   \end{cvitems}
    }

\end{cventries}
